Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-06-15 completeness.tex
after discussion about completeness with Naeem, years changed

\begin{table}%[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
        \cline{2-7}                                              \\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & 
                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
        \hline                                                   \\[-1.6ex]
        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:completeness} 
\end{table}

>>>>

\begin{table}%[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
        \cline{2-7}                                              \\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & 
                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
        \hline                                                   \\[-1.6ex]
        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
        Alborz          & 2005 & 1961 & 1900 & 1664 &--401 & 4.4 \\
        Kopeh Dagh      & 2005 & 1950 & 1924 & 1673 &    9 & 4.5 \\
        Zagros          & 2005 & 1961 & 1950 & 1853 & 1439 & 4.4 \\
        Central-East    & 2005 & 1961 & 1900 & 1837 &  762 & 4.5 \\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:completeness} 
\end{table}
